Methods to prioritise pop-up active transport infrastructure

### 2020-05-10 article.Rmd

<!-- The COVID-19 pandemic has transformed all sectors of the economy, not least transport. -->
<!-- [Demand for long distance trips has plummetted](https://osf.io/preprints/socarxiv/v3g5d/) and [airline companies have gone bust](https://arxiv.org/abs/2004.08460) [@iacus_estimating_2020; @jittrapirom_exploratory_2020]. -->
Much attention has focused on the impacts of COVID-19 on long-distance travel patterns [e.g. @iacus_estimating_2020; @jittrapirom_exploratory_2020].
Yet short distance travel patterns have also changed, with a notable increase in active travel, particularly cycling, in some areas  [@harrabin_boom_2020].
The two main explanations for this are 1) the need increased need for exercise close to home during lockdowns for mental and physical health [@jimenez-pavon_physical_2020], and 2) a reduction in both public transport options and use [e.g. @tian_investigation_2020].
The second reason is particularly important given that many' key workers' are low paid, with limited access to private automobiles.

@@

- Estimates of cycling potential to work at the street segment level from the UK Department for Transport funded Propensity to Cycle Tool (PCT) project [@goodman_scenarios_2019; @lovelace_propensity_2017; @R-pct]
- Data derived from OpenStreetMap, with several new variables added to support cycling infrastructure planning (see www.cyipt.bike for an overview)
- A list hospital locations from the UK's National Health Service website [www.nhs.uk](https://www.nhs.uk/about-us/nhs-website-datasets/)
<!-- - Data on the location of road traffic casualties from -->

@@

<!-- Note this could be a function in an R packge.. -->
<!-- see https://github.com/cyipt/cyipt/blob/82248b2f99e388fac314d34ec5aa49bb90a737a3/scripts/prep_data/clean_osm.R#L349 -->

@@

The results of the method are summarised in Figure \@ref(fig:res) and Table 2.
We have found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing the 85,000 road segments for Leeds down to candidate segments with more than 1 lane near key destinations that can be visualised in an interactive map can has great potential to support policy-makers, especially when decisions need to be made fast.

>>>>

<!-- The COVID-19 pandemic has transformed all sectors of the economy, not least transport. -->
<!-- [Demand for long distance trips has plummetted](https://osf.io/preprints/socarxiv/v3g5d/) and [airline companies have gone bust](https://arxiv.org/abs/2004.08460) [@iacus_estimating_2020; @jittrapirom_exploratory_2020]. -->
Much attention has focused on the impacts of COVID-19 on long-distance travel patterns [e.g. @iacus_estimating_2020; @jittrapirom_exploratory_2020].
Yet short distance travel patterns have also changed, with a notable increase in active travel, particularly cycling, in some areas  [@harrabin_boom_2020].
The two main explanations for this are 1) the need increased need for exercise close to home during lockdowns for mental and physical health [@jimenez-pavon_physical_2020], and 2) a reduction in both public transport options and use [e.g. @tian_investigation_2020].
The second reason is particularly important given that many 'key workers' are low paid, with limited access to private automobiles.

@@

- Estimates of cycling potential to work at the street segment level from the UK Department for Transport funded Propensity to Cycle Tool (PCT) project [@goodman_scenarios_2019; @lovelace_propensity_2017; @R-pct]
- Data derived from OpenStreetMap, with several new variables added to support cycling infrastructure planning (see www.cyipt.bike for an overview)
- A list of hospital locations from the UK's National Health Service website [www.nhs.uk](https://www.nhs.uk/about-us/nhs-website-datasets/)
<!-- - Data on the location of road traffic casualties from -->

@@

<!-- Note this could be a function in an R package.. -->
<!-- see https://github.com/cyipt/cyipt/blob/82248b2f99e388fac314d34ec5aa49bb90a737a3/scripts/prep_data/clean_osm.R#L349 -->

@@

The results of the method are summarised in Figure \@ref(fig:res) and Table 2.
We have found that analysis of open transport network data, alongside careful selection of parameters, can generate plausible results for the prioritisation of pop-up cycle infrastructure.
Reducing the 85,000 road segments for Leeds down to candidate segments with more than 1 lane near key destinations that can be visualised in an interactive map has great potential to support policy-makers, especially when decisions need to be made fast.
